---
title: "120 years of Olympic history: Data Visualization"
author: "Min-Jhen Wu"
date: "2021/10/10"
output:
  html_document: default
  pdf_document: default
---

 Find interesting dataset and prepare short report (in R Markdown) which will 
 consists:
* short description of the dataset,
* 3 scatterplots which will present interesting relationships between variables,
* brief comments which describes obtained results.

 Please remember about:
- using different aesthetics to show properly the insights from the data
- adding smoothing line
- labeling graph with proper title, subtitle and description of the axis.

The deadline for the homework is until next classes and cannot be postponed under any circumstances.

## Introduction
Boston Housing Data consists of price of house in suburbs of Boston. 

Boston Housing Data comes with the MASS library.

Source: https://www.kaggle.com/heesoo37/120-years-of-olympic-history-athletes-and-results

## Data Variables
- ID: Unique number for each athlete
- Name:Athlete's name
- Sex:Male or Female
- Age:Athlete's age in integer
- Height:Athlete's height in centimeters
- Weight: Athlete's weight in kilograms
- Team: Team name
- NOC: National Olympic Committee 3-letter code
- Games: Year and season
- Year: Integer
- Season: Summer or Winter
- City: Host city
- Sport: Sport
- Event: Event
- Medal: Gold, Silver, Bronze, or NA

The Winter and Summer Games were held in the same year up until 1992. After that, they staggered them such that Winter Games occur on a four year cycle starting with 1994, then Summer in 1996, then Winter in 1998, and so on.



```{r}

library(ggplot2)
library(dplyr)
library(tidyr)

athlete <- read.csv('/Users/jeank4723/Desktop/Advance VR/1/Data/athlete_events.csv')

head(athlete)

athlete$Sex <- as.factor(athlete$Sex)
athlete$Season <- as.factor(athlete$Season)
athlete$Medal <- as.factor(athlete$Medal)

str(athlete)

```

```{r}

# 
# sum_of_na <- function(x){
#   sum(is.na(x))
# }
# athlete %>% summarise(
#   across(everything(), sum_of_na)
# )

```


## 3 Scatterplots

1. Year and Height
We can see that the height range of athletes is increasing year by year. Also, compare the close and far year from now, there were more female in Olympic than beginning.

```{r}
tyeatdata <- cut(athlete$Year, breaks = seq(1896,2016, by = 20), dig.lab = 4)
p1 <- ggplot(data = athlete, aes(x = tyeatdata,
                           y = Height,
                           color = Sex
                           ))
p1 + geom_point()
```
2. Year and Age
The age of athletes are not much different from and then. However, we can observe that more female athletes in the age 25 to 50 are more the before since 1980.

```{r}
p2 <- ggplot(data = athlete, aes(x = Year,
                           y = Age,
                           color = Sex
                           ))
p2 + geom_point()
```
3. Medal and BMI
Using the Height and Weight data to use the BMI (Body mass index) formula: Weight in kilograms divided by Height in meters squared. According to Wikipedia, the table of meaning of the value for adult. 

### BMI Categories:
- Underweight = <18.5
- Normal weight = 18.5–24.9
- Overweight = 25–29.9
- Obesity = BMI of 30 or greater

We can observe that there is no obvious differ from each medal winners.

```{r}

BMIdata <- athlete  %>% 
  mutate(BMI = Weight/(Height*Height*0.0001))
  
p3 <- ggplot(data = BMIdata, aes(x = Medal,
                           y = BMI,
                           color = Sex
                           ))
p3 + geom_point()
```

